Clone and graft:\\ Testing scientific applications as they are built

### 2015-01-14 turcksin-spring-mechanics/paper.tex
Add acknowledgments.

\marginpar{Acknowledgments}

>>>>

\paragraph*{Acknowledgments}
B.~Turcksin and W.~Bangerth were partially supported by the National Science
Foundation under award OCI-1148116 as part of the Software Infrastructure for
Sustained Innovation (SI2) program; by the Computational
Infrastructure in Geodynamics initiative (CIG), through the National Science
Foundation under Award No.~EAR-0949446 and The University of California --
Davis.
\marginpar{Timo -- please update.}
